A Survey of Exoskeleton Control (Draft 1.1)

### 2015-09-18 paper.tex
add latex-commands.tex

@@

>>>>

\subsection{Reference Design: linear pneumatic}

Survey state of the art using linear pneumatic actuators:

\begin{verbatim}
07139975
2015 IEEE International Conference on Robotics and Automation (ICRA)
Towards Balance Recovery Control for Lower Body Exoskeleton Robots
with Variable Stiffness Actuators: Spring-Loaded Flywheel Model
Corinne Doppmann, Barkan Ugurlu, Masashi Hamaya, Tatsuya Teramae,
Tomoyuki Noda, and Jun Morimoto
\end{verbatim}

@@

Different types of actuation can be combined: springs and electric motors,
for example. This combination can also be viewed as combining energy
storage and actuation. Slow pneumatics and fast electric motors~\cite{Morimoto,UCLA}.
Mini/Macro~\cite{Stanford}.
